---
title: "Week 48 Assignment"
author: "Mark Nickelsen"
date: "2022-12-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```
Run
```{r startup, include=FALSE}
library(leaflet)
library(htmlwidgets)
```

Read the csv file
```{r Reading csv file, include=TRUE}
SuperligaStadiums <- read.csv("data/SuperligaStadiums.csv")
```
## Task 1 and 2. Visualizing The Superliga Stadiums on a Map

```{r Visualization, include=TRUE}
Denmark <- leaflet() %>%   # assign the base location to an object
  setView(10.5, 56, zoom = 6)

# Now, prepare to select backgrounds
esri <- grep("^Esri", providers, value = TRUE)

for (provider in esri) {
  Denmark <- Denmark %>% addProviderTiles(provider, group = provider)
  
}

DANmap <- Denmark %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright")

DANmap
```


Now we diplay the map and input the markers

```{r input markers, include=TRUE}
StadiumMap<-DANmap %>% 
  addMarkers(lng = SuperligaStadiums$Longitude, 
             lat = SuperligaStadiums$Latitude,
             popup = SuperligaStadiums$Description)


StadiumMap
```

## Task 3: Can you cluster the points in Leaflet? Google "clustering options in Leaflet"

To Cluster the markers, we add the cluster command to the previous command

```{r Clustering, include=TRUE}
StadiumMap<-DANmap %>% 
  addMarkers(lng = SuperligaStadiums$Longitude, 
             lat = SuperligaStadiums$Latitude,
             popup = SuperligaStadiums$Description,
             clusterOptions=markerClusterOptions())


StadiumMap
```


## Task 4: Look at the map and consider what it is good for and what not.
As we can see, Clustering help us organize our map markers, which is especially noticeable stadiums around Copenhagen

## Task 5: Find out how to display notes and classifications in the map.

Since my document dont have note and classifications, i here instead use the label
command to display the Superliga stadium placenames

```{r Labeling, include=TRUE}
StadiumMap<-DANmap %>% 
  addMarkers(lng = SuperligaStadiums$Longitude, 
             lat = SuperligaStadiums$Latitude,
             popup = SuperligaStadiums$Description,
             clusterOptions=markerClusterOptions(),
             label = SuperligaStadiums$Placename)
StadiumMap
```

Now we can hover the mouse above the Markers and see the Stadium names






